\cleardoublepage{}
\begin{center}
    \bfseries \zihao{3} 摘~要
\end{center}

目前，对于手指运动追踪系统来说，基于视觉的系统具有高跟踪精度的主要优势。然而，它们也存在一些限制，包括对光照条件变化和遮挡问题的敏感性。此外，基于视觉的系统通常体积庞大且昂贵。
基于传感器的系统则利用各种传感器。这些系统在缓解基于视觉系统存在的一些问题方面具有优势。然而，基于传感器的系统也面临着自身的挑战，例如重力干扰、耐久性有限等。

与其他类型的传感器相比，基于磁传感器的手指运动追踪装置可以利用各种信号源。通过将磁传感器与加速度计、陀螺仪和其他类型的传感器结合使用，可以进一步提高追踪系统的性能。
综合起来，本文开发了一种利用多个磁传感器和惯性传感器的，低成本、高灵敏度、紧凑的智能手指运动追踪系统，并同时具有实时手势识别功能。此外，深度学习技术也被积极探索和应用，以提高实时手势识别的准确性。
本文同时结合了多传感器配置和深度学习技术，为最终设计出具有较好的灵敏度、较高的准确性和较强的经济性的多功能手指运动追踪系统提供了一定的基础参考。该系统在虚拟现实、增强现实、人机交互和生物医学工程等各个领域都有潜在的应用前景。

{\noindent \textbf{关键词：} 磁传感器；手指追踪；手势识别；深度学习；多传感器}

\cleardoublepage{}
\begin{center}
    \bfseries \zihao{3} Abstract
\end{center}

Currently, for finger motion tracking systems, vision-based systems offer the main advantage of high tracking accuracy. However, they have some limitations, including sensitivity to variations in lighting conditions and occlusion issues. 
Additionally, vision-based systems are often bulky and expensive.
Sensor-based systems utilize a variety of sensors. These systems offer advantages in mitigating some of the issues present in vision-based systems.
However, sensor-based systems have their own challenges, such as gravity interference, limited durability, and so on.

Compared to other types of sensors, magnetic sensors offer the possibility of measuring higher precision degrees of freedom due to their diversity. A finger motion detection device based on magnetic sensors can utilize various signal sources.
By combining magnetic sensors with accelerometers, gyroscopes, and other types of sensors, the performance of the detection system can be further enhanced.
Therefore, this project has developed a low-cost, highly sensitive, and compact finger motion detection system using multiple magnetic sensors and inertial sensors. Additionally, deep learning techniques have been actively explored and applied to enhance the detection accuracy.
The combination of a multi-sensor setup and deep learning techniques in this project contributes to a comprehensive finger motion detection system that offers high sensitivity, accuracy, and cost-effectiveness. This system has the potential to find applications in various domains such as virtual reality, augmented reality, human-computer interaction, and biomedical engineering.

{\noindent \textbf{Key words:} magnetic sensor; finger tracking; gesture recognition; deep learning; multiple sensors}